Global adjoint tomography -- Model GLAD-M25

### 2018-09-28 main.tex

  We want to give thanks to the Oak Ridge National Lab, for providing
  excellent support and computational resource that facilitate our research.
  We want to thanks IRIS and ORFEUS for providing seismic datas used in this
  study. We want to acknowledge Hejun Zhu, Min Chen, Carl Tape and Qinya Liu,
  for providing usefull tools and great suggetions these years.
  We want to thanks Ebru Bozdag, for providing GLAD-M15, data and software
  she used in the first generation model.

>>>>

%We want to give thanks to the Oak Ridge National Lab, for providing
%  excellent support and computational resource that facilitate our research.
%  We want to thanks IRIS and ORFEUS for providing seismic datas used in this
%  study. We want to acknowledge Hejun Zhu, Min Chen, Carl Tape and Qinya Liu,
%  for providing usefull tools and great suggetions these years.
%  We want to thanks Ebru Bozdag, for providing GLAD-M15, data and software
%  she used in the first generation model.

This research used resources of the Oak Ridge Leadership Computing Facility, which is a DOE Office of Science User Facility supported under contract DE-AC05-00OR22725.
Additional computational resources were provided by the Princeton Institute for Computational Science \& Engineering (PICSciE).
We acknowledge IRIS ({\tt iris.edu}) and ORFEUS ({\tt orfeus-eu.org}) for providing the data used in this study. We thank Ryan Modrak, Ridvan Orsvuran, Frederik Simons, and James Smith for fruitful discussions.
The open source spectral-element software package SPECFEM3D\_GLOBE and the seismic measurement software package FLEXWIN used for this article are freely available via the Computational Infrastructure for Geodynamics (CIG; {\tt geodynamics.org}). This research was supported by NSF grant~1644826.
